---
title: "Data Wrangling"
author: "Preethi Aranala"
---
# 1.0 LIBRARIES ----
<<<<<<< Updated upstream
```{r}
#| eval: false
#| 
=======
>>>>>>> Stashed changes

library(dplyr)
library(vroom)
library(ggplot2)
<<<<<<< Updated upstream
```

# 2.0 ASSIGNING COLUMN TYPES
```{r}
#| eval: false
#| 

=======
library(data.table)
# 2.0 ASSIGNING COLUMN TYPES
>>>>>>> Stashed changes
col_types <- list(
  id = col_character(),
  patent_id = col_character(),
  assignee_id = col_character(),
  mainclass_id = col_character(),
  type = col_character(),
  number = col_character(),
  country = col_character(),
  organization = col_character(),
  date = col_date("%Y-%m-%d"),
  abstract = col_character(),
  title = col_character(),
  kind = col_character(),
  num_claims = col_double(),
  filename = col_character(),
  withdrawn = col_double(),
  sequence = col_integer()
)
<<<<<<< Updated upstream
```
# 3.0 IMPORTING FILES INTO TABLES
```{r}
#| eval: false
#| 

patent_tbl <- vroom(
            file       = "00_raw_data/Patent_data_reduced/patent.tsv", 
=======

# 3.0 IMPORTING FILES INTO TABLES
patent_tbl <- vroom(
            file       = "C:/Users/Preethi Aranala/OneDrive/Documents/GitHub/ss23-bdsb-PreethiAranala/content/Patent_data_reduced/Patent_data_reduced/patent.tsv", 
>>>>>>> Stashed changes
            delim      = "\t", 
            col_types  = col_types[c("id",  "date",  "num_claims")],
            na         = c("", "NA", "NULL")
        )

patent_assignee_tbl <- vroom(
<<<<<<< Updated upstream
            file       =  "00_raw_data/Patent_data_reduced/patent_assignee.tsv", 
=======
            file       =  "C:/Users/Preethi Aranala/OneDrive/Documents/GitHub/ss23-bdsb-PreethiAranala/content/Patent_data_reduced/Patent_data_reduced/patent_assignee.tsv", 
>>>>>>> Stashed changes
            delim      = "\t", 
            col_types  = col_types[c("patent_id",   "assignee_id")],
            na         = c("", "NA", "NULL")
        )
        
assignee_tbl        <- vroom(
<<<<<<< Updated upstream
            file       = "00_raw_data/Patent_data_reduced/assignee.tsv", 
=======
            file       = "C:/Users/Preethi Aranala/OneDrive/Documents/GitHub/ss23-bdsb-PreethiAranala/content/Patent_data_reduced/Patent_data_reduced/assignee.tsv", 
>>>>>>> Stashed changes
            delim      = "\t", 
            col_types  = col_types[c("id",  "type",  "organization")],
            na         = c("", "NA", "NULL")
        )
        
uspc_tbl            <- vroom(
<<<<<<< Updated upstream
            file       =  "00_raw_data/Patent_data_reduced/uspc.tsv", 
=======
            file       =  "C:/Users/Preethi Aranala/OneDrive/Documents/GitHub/ss23-bdsb-PreethiAranala/content/Patent_data_reduced/Patent_data_reduced/uspc.tsv", 
>>>>>>> Stashed changes
            delim      = "\t", 
            col_types  = col_types[c("patent_id",  "mainclass_id",                                              "sequence")],
            na         = c("", "NA", "NULL")
        )
<<<<<<< Updated upstream
```

# 3.1 Question 1
# 3.1.1 Manipulating the data        
```{r}
#| eval: false
#| 
=======
# 3.1 Question 1
# 3.1.1 Manipulating the data        
>>>>>>> Stashed changes

patent_assignee_dt <- merge(patent_assignee_tbl, assignee_tbl, by.x = "assignee_id", by.y = "id", all.x = T) %>%
        filter(type == 2) %>% 
        group_by(organization) %>%
        summarize(quantity = n()) %>%
        arrange(desc(quantity))
<<<<<<< Updated upstream
```

# 3.1.2 Visualizing the data       
```{r}
#| eval: false
#| 
=======
        
# 3.1.2 Visualizing the data       
>>>>>>> Stashed changes
patent_assignee_dt %>%
        slice(1:10) %>%
        ggplot(aes(x=organization, y=quantity)) +
        geom_label(aes(label = quantity), vjust = -0.2) + 
        geom_col(fill = "#2DC6D6") + 
        theme(axis.text.x = element_text(angle = 45, hjust = 1))+ 
labs(
    title    = "Patents by Top US Companies",
    x = "Top 10 US Companies", # Override defaults for x and y
    y = "Quantity"
  )
<<<<<<< Updated upstream
``` 
# 3.2.1
```{r}
#| eval: false
#| 
=======
 
# 3.2.1

>>>>>>> Stashed changes
patent_dt2 <- patent_tbl %>%
        left_join(patent_assignee_tbl, by = c("id" = "patent_id")) %>%
        left_join(assignee_tbl, by = c("assignee_id" = "id")) %>%
        filter(type == 2 & date>= "2014-08-01" & date<= "2014-08-31") %>% 
        group_by(organization) %>%
        summarise(quantity = n()) %>%
        ungroup() %>%
        arrange(desc(quantity))
<<<<<<< Updated upstream
```        
# 3.2.2 Visualizing the data       
```{r}
#| eval: false
#| 
=======
        
# 3.2.2 Visualizing the data       
>>>>>>> Stashed changes
patent_dt2 %>%
        slice(1:10) %>%
        ggplot(aes(x=organization, y=quantity)) +
        geom_label(aes(label = quantity), vjust = -0.2) + 
        geom_col(fill = "#2DC6D6") + 
        theme(axis.text.x = element_text(angle = 45, hjust = 1))+ 
labs(
    title    = "Most Patents by Top US Companies in August 2014",
    x = "Top 10 US Companies", # Override defaults for x and y
    y = "Quantity"
  )
<<<<<<< Updated upstream
```
# 3.3.1
```{r}
#| eval: false
#| 
=======

# 3.3.1

>>>>>>> Stashed changes
patent_dt3 <- patent_assignee_tbl %>%
        left_join(assignee_tbl, by = c("assignee_id" = "id"), relationship = "many-to-many") %>%
        left_join(uspc_tbl, by = c("patent_id" = "patent_id"), relationship = "many-to-many")
        
top_10_companies <- patent_dt3 %>%
  group_by(organization) %>%
  summarise(num_patents = n()) %>%
  top_n(10, num_patents)

top_5_USPTO <- patent_dt3 %>%
  filter(organization %in% top_10_companies$organization) %>%
  group_by(mainclass_id) %>%
  summarise(num_patents_per_mainclass = n()) %>%
  na.omit() %>%
  top_n(5,num_patents_per_mainclass)
<<<<<<< Updated upstream
```
# 3.3.2
```{r}
#| eval: false
#| 
=======
>>>>>>> Stashed changes

top_5_USPTO %>%
        ggplot(aes(x=mainclass_id, y=num_patents_per_mainclass)) +
        geom_label(aes(label = num_patents_per_mainclass), vjust = -0.2) + 
        geom_col(fill = "#2DC6D6") + 
        theme(axis.text.x = element_text(angle = 45, hjust = 1))+ 
labs(
    title    = "Top 5 USPTO Classes by Top 10 Companies",
    x = "Main Class ID", # Override defaults for x and y
    y = "Quantity"
  )
<<<<<<< Updated upstream
```
=======

>>>>>>> Stashed changes

